We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-06 paper/paper.tex
edit

The fits to the multivariate gaussian distributions can be used now to
compute the expected number of pairs with characteristics similar to
the LG.
To do this we generate $10^3$ samples, each sample contains $10^4$
pairs which are drawn from the multivariate gaussian distributions.

Figure \ref{fig:expected_number} summarizes the results from this
experiment. 
The left panel

>>>>

The fits to the multivariate gaussian distributions can be used now to
compute the expected number of pairs with characteristics similar to
the LG.
To do this we generate $10^3$ samples, each sample contains $10^4$
pairs, where each pair member is drawn from the corresponding
multivariate gaussian distributions.

Figure \ref{fig:expected_number} summarizes the results from this
experiment. 
The left panel shows the probability density for the number of M31
systems in a parent sampe of $10^4$ pairs, the right panel shows the
results for the MW.

We consider that a sampled system is similar to the M31/MW galaxy if the
distance of each of its characteristics ($w$, $c/a$, $b/a$) to the
sample mean is larger than the distance of the observational values to
the sample mean. 
That is, we perform a double-tailed test using the observational
values as a threshold.

Under this conditions
